Structured Versus Decorated Cospans

### 2021-06-17 cospans_new.tex
completed proofs of Thms. 2.1 and 2.2

We start with decorated cospans, proving Theorems \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built
from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.    The Grothendieck construction gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations $U \maps \inta F \to \A$.  We need two refinements of this construction: one that gives monoidal ofibrations, and one that gives symmetric monoidal opfibrations.  We explain the Grothendieck construction and all these related concepts in \cref{subsec:fibrations}; here we simply recall the result we need.

@@

Now we are ready to use Shulman's result to prove  \cref{thm:decorated_cospans_1} and  \cref{thm:decorated_cospans_2}.

\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
To obtain the desired double category we apply \cref{lem:shulman} to a bifibration $\Phi \maps \A/U \to \A$ which we now define.   Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$.  As in \cref{def:GrothCat},
\begin{itemize}
\item an object of $\inta F$ is a pair $(b,x)$ where $b \in \A$ and $x \in F(b)$;
\item a morphism in $\inta F$ from $(b,x)$ to $(b',x')$ is a pair $(g,h)$
where $g \maps b \to b'$ is a morphism in $\A$ and $h \maps F(g)(x) \to x'$ is
a morphism in $F(b')$.
\end{itemize}
The functor $U$ maps objects and morphisms to their first component, so one can describe
the comma category $\A/U$ as follows:
\begin{itemize}
\item an object is a pair $(a \xrightarrow{i} b, x)$ consisting of a morphism in $\A$ and an
object $x \in F(b)$;
\item a morphism from $(a \xrightarrow{i} b, x)$ to $(a' \xrightarrow{i'} b', x')$ is a triple $(f,g,h)$ where $f \maps a \to a'$ and $g \maps b \to b'$ are morphisms in $\A$ such that this square commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$a'$};
\node (C) at (0,-1) {$b$};
\node (D) at (1.5,-1) {$b'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$i$} (C)
(B) edge node[right]{$i'$} (D)
(C) edge node[below]{$g$} (D);
\end{tikzpicture}
\]
and $h \maps F(g)(x) \to x'$ is a morphism in $F(b')$.
\end{itemize}
As in any comma category we have a functor $\Phi \maps \A/U \to \A$; this is given on objects by $\Phi(a \xrightarrow{i} b, x)=a$ and on morphisms by $\Phi(f,g,h)=f$.

There is a monoidal structure on $\A/U$ coming from the monoidality of $U$.  On objects
this is given by
\[  (a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x') = (a+a' \xrightarrow{i+i'} b+b', 
\phi_{a,b}(d,d') )\]
where $\phi$ is the laxator for $F$.  The monoidal unit is given by $(0_\A \xrightarrow{!} 0_\A, x)$
where $x \in F(0_\A)$ is the element given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure it is easy to check that the functor $\Phi$ is strict monoidal.

One can check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', x') \in \A/U$ over $a'$, a cartesian lifting of $f$ is given by 
\[ (f,1,1) \maps (a \xrightarrow{i' f} b' , x')\; \to \; (a' \xrightarrow{i'} b', x'). \]
Denoting this cartesian lifting by $\textnormal{cart}(f)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.

@@

\iffalse
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (2.5,0) {$c$};
\node (C) at (1.5,1) {$a'$};
\node (D) at (0,-2) {$U(x)$};
\node (E) at (2.5,-2) {$U(y)$};
\node (F) at (1.5,-1) {$U(x') = U(x)+_a a'$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above] {$\theta$} (F)
(F) edge [dashed] node [right] {$\exists ! \psi$} (E)
(D) edge node [above] {$U(g')$} (E)
(A) edge node [left] {$i$} (D)
(C) edge node [right,near end] {$i'$} (F)
(B) edge node {$$} (E)
(A) edge node[above]{$f'$} (B)
(C) edge node [right] {$p$} (B)
(A) edge node[left]{$f$} (C);
%(B) edge [dashed] node[right]{$$} (D)
%(C) edge [dashed] node[above]{$$} (D);
\end{tikzpicture}
\]
\fi

Lastly, we need to check that $\Phi$ satisfies the Beck--Chevalley condition. Given a pushout square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$b$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$d$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$g$} (D)
(C) edge node[below]{$f$} (D);
\end{tikzpicture}
\]
we need to show that the natural transformation $\theta$, defined as in \cref{subsec:fibrations}, is an isomorphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)_a$};
\node (B) at (1.5,0) {$(\A/U)_b$};
\node (C) at (0,-1) {$(\A/U)_c$};
\node (D) at (1.5,-1) {$(\A/U)_d$.};
\node (E) at (0.75,-0.5) {$\Searrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge node[above]{$h^*$} (A)
(A) edge node[left]{$k_!$} (C)
(B) edge node[right]{$g_!$} (D)
(D) edge node[below]{$f^*$} (C);
\end{tikzpicture}
\]
Let $(b \xrightarrow{i} e, x)$ be an object of $(\A/U)_b$. Going left, we precompose with $h \maps a \to b$ to obtain the object $(a \xrightarrow{i \circ h} e, z)$ of $(\A/U)_a$. Then going down, we push forward along $k$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$e$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$c+_{a}e$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i \circ h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\psi$} (D);
\end{tikzpicture}
\]
to obtain the object $(c \xrightarrow{\psi} c+_a e, F(\psi)(x))$ of $(\A/U)_c$.
%and so by construction, we have that 
%\[  U(z)=U(\bot_c+_{\bot_a}x)=c+_a U(x).\]
%{\john Need to refer to a proposition where we show $U$ preserves pushouts strictly.}
 For the other route, first going down, we push the object $(b,x,b \xrightarrow{i} U(x))$ forward along $g \maps b \to d$ by taking the following pushout:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$b$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$d$};
\node (D) at (1.5,-1) {$d+_{b}U(x)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(A) edge node[left]{$g$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\theta$} (D);
\end{tikzpicture}
\]
which yields the object $(d,z',d \xrightarrow{\theta} U(z'))$ of $(\A/U)_d$ where $z' \in \A \times F(d+_b U(x))$ is given by ${z'=(d+_b U(x),q')}$ where $q'$ is given by 
\[ 1 \xrightarrow{p} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_d +_{!_b} 1)} F(d+_b U(x)). \]
We then precompose with $f \maps c \to d$ to obtain the object $(c,z',c \xrightarrow{\theta \circ f} U(z'))$ of $(\A/U)_c$.

Now we seek a natural isomorphism between the two objects $(c,z,c \xrightarrow{\psi} c+_a U(x))$ and $(c,z',c \xrightarrow{\theta \circ f} d+_b U(x))$ in $(\A/U)_c$. It suffices to obtain a natural isomorphism between the two objects $z$ and $z'$ in $\X$. This pushout square:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$c+_{a}U(x)$};
%\node (A') at (4,0) {$L(b)$};
%\node (B') at (6,0) {$x$};
%\node (C') at (4,-1) {$L(d)$};
%\node (D') at (6,-1) {$L(d)+_{L(b)}x$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i \circ h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\psi$} (D);
%(A') edge node[above]{$I$} (B')
%(A') edge node[left]{$L(g)$} (C')
%(B') edge node[right]{$$} (D')
%(C') edge node[below]{$\theta$} (D');
\end{tikzpicture}
\]
exhibits $c+_a U(x)$ as a pushout of the span 
\[  c \xleftarrow{k} a \xrightarrow{i \circ h} U(x) 
\]
in $\A$. We may also take the first pushout square above and paste it with the original pushout square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$b$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$d$};
\node (D) at (1.5,-1) {$d+_{b}U(x)$};
\node (E) at (-1.5,0) {$a$};
\node (F) at (-1.5,-1) {$c$};
\path[->,font=\scriptsize,>=angle 90]
(E) edge node [left] {$k$} (F)
(E) edge node [above] {$h$} (A)
(F) edge node [below] {$f$} (C)
(A) edge node[above]{$i$} (B)
(A) edge node[left]{$g$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\theta$} (D);
\end{tikzpicture}
\]
obtaining a pushout square 
which exhibits $d+_b U(x)$ as a pushout of the same span in $\A$.  The resulting natural isomorphism $\kappa$ between $c+_a U(x)$ and $d+_b U(x)$ then extends to a natural isomorphism between $z=(c+_a U(x),q)$ and $z'=(d+_b U(x),q')$ in $\X$:
\[
\begin{tikzpicture}[scale=1.5]
\node () at (5,0) {$\cong$};
\node (A) at (0,0) {$1$};

\node (A1) at (2,0.5) {$F(U(x))$};
\node (A2) at (4,0.5) {$F(0+_0 U(x))$};
\node (A3) at (6,0.5) {$F(c+_a U(x))$};

\node (B1) at (2,-0.5) {$F(U(x))$};
\node (B2) at (4,-0.5) {$F(0+_0 U(x))$};
\node (B3) at (6,-0.5) {$F(d+_b U(x))$};

\path[->,font=\scriptsize,>=angle 90]
(A) edge node[fill=white]{$p$} (A1)
(A) edge node[fill=white]{$p$} (B1)

(A1) edge node [above] {$F(\zeta)$} (A2)
(A2) edge node [above] {$F(!_c +_{!_a} 1)$} (A3)

(A1) edge node [fill=white] {$1$} (B1)
(A2) edge node [fill=white] {$1$} (B2)
(A3) edge node [fill=white] {$F(\kappa)$} (B3)

(B1) edge node [above] {$F(\zeta)$} (B2)
(B2) edge node [above] {$F(!_d +_{!_b} 1)$} (B3);

\end{tikzpicture}
\]
and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $\Phi$ satisfies the Beck--Chevalley condition.

Having checked the hypotheses of \cref{lem:shulman}, we then define $F\lCsp$ to be $\Fr(\Phi)$.
\end{proof}

@@

A functor $\Phi \maps \X \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.      If $\X$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \maps \X \to \A$ is a bifibration that is also a strict monoidal functor, such that the tensor product of $\A$ preserves cartesian and cocartesian liftings.   Similarly, if $\C$ and $\A$ are symmetric monoidal, a \define{symmetric monoidal} bifibration is a bifibration $\Phi \maps \C \to \A$ that is a symmetric strict monoidal functor.

>>>>

We start with decorated cospans, proving Theorems \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built
from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.    The Grothendieck construction gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations $U \maps \inta F \to \A$.  We need two refinements of this construction: one that gives monoidal ofibrations, and one that gives symmetric monoidal opfibrations.  We explain the Grothendieck construction and these related concepts in \cref{subsec:fibrations}; here we simply recall the result we need.

@@

Now we are ready to use Shulman's result to prove  \cref{thm:decorated_cospans_1} and  \cref{thm:decorated_cospans_2}.  An $F$-decorated cospan from $a \in \A$ to $b \in \A$
is a cospan 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b$};
%\node (D) at (2.6,0) {$x \in F(m))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B);
\end{tikzpicture}
\]
in $\A$ together with an object $x \in F(m)$.   This can be seen as a pair $(e \to m, x \in F(m))$ such that $e$ equals $a + b$.   But $(m,x \in F(m))$ is precisely an object of the Grothendieck category $\inta F$, and the opfibration $U \maps \inta F \to \A$ sends this object to $m$.  Thus, $(e \to m, x \in F(m))$ can be seen as an object of the comma category $\A/U$.   Let $\Phi \maps \A/U \to \A$ be the functor sending any object $(e \to m,x \in F(m)) \in \A/U$ to $e$.  Then an $F$-decorated cospan from $a$ to $b$ amounts to an object $c \in \A/U$ such that $\Phi(c) = a + b$.    With this choice of $\Phi$, Shulman's result gives the double category of $F$-decorated cospans.

\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$.  To obtain the desired double category we apply Shulman's \cref{lem:shulman} to the functor $\Phi \maps \A/U \to \A$, which we now describe in more detail.  In the comma category $\A/U$:
\begin{itemize}
\item an object is a pair $(a \xrightarrow{i} b, x)$ consisting of a morphism in $\A$ and an
object $x \in F(b)$;
\item a morphism from $(a \xrightarrow{i} b, x)$ to $(a' \xrightarrow{i'} b', x')$ is a triple $(f,g,h)$ where $f \maps a \to a'$ and $g \maps b \to b'$ are morphisms in $\A$ such that this square commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$a'$};
\node (C) at (0,-1) {$b$};
\node (D) at (1.5,-1) {$b'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$i$} (C)
(B) edge node[right]{$i'$} (D)
(C) edge node[below]{$g$} (D);
\end{tikzpicture}
\]
and $h \maps F(g)(x) \to x'$ is a morphism in $F(b')$.
\end{itemize}
As in any comma category we have a functor $\Phi \maps \A/U \to \A$; this is given on objects by $\Phi(a \xrightarrow{i} b, x)=a$ and on morphisms by $\Phi(f,g,h)=f$.

To apply \cref{lem:shulman} it suffices to prove that $\Phi$ is a Beck--Chevalley monoidal opfibration.   First, there is a monoidal structure on $\A/U$ coming from the monoidality of $U$.  On objects this is given by
\[  (a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x') = (a+a' \xrightarrow{i+i'} b+b', 
\phi_{a,b}(d,d') )\]
where $\phi$ is the laxator for $F$.  The monoidal unit is $(0_\A \xrightarrow{!} 0_\A, x)$
where $x \in F(0_\A)$ is the element given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure it is easy to see that $\Phi$ is strict monoidal.

Next, one can check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', x') \in \A/U$ over $a'$, a cartesian lifting of $f$ is given by 
\[ (f,1,1) \maps (a \xrightarrow{i' f} b' , x')\; \to \; (a' \xrightarrow{i'} b', x'). \]
Denoting this cartesian lifting by $\textnormal{cart}(f)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.

@@

Lastly, we need to check that $\Phi$ satisfies the Beck--Chevalley condition.  Merely from the fact that $\Phi$ is a bifibration, for any commutative square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$b$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$d$};
\label{bc-square}
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$g$} (D)
(C) edge node[below]{$f$} (D);
\end{tikzpicture}
\]
there is a natural transformation
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)_a$};
\node (B) at (1.5,0) {$(\A/U)_b$};
\node (C) at (0,-1) {$(\A/U)_c$};
\node (D) at (1.5,-1) {$(\A/U)_d$.};
\node (E) at (0.75,-0.5) {$\Searrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge node[above]{$h^*$} (A)
(A) edge node[left]{$k_!$} (C)
(B) edge node[right]{$g_!$} (D)
(D) edge node[below]{$f^*$} (C);
\end{tikzpicture}
\]
as defined at the end of \cref{subsec:fibrations}.   We need to prove that when the square in $\A$ is 
a pushout, $\theta$ is a natural isomorphism.

We start by describing $\theta$ more concretely.  Let $(b \xrightarrow{i} e, x)$ be an object of $(\A/U)_b$. Going left, we precompose with $h \maps a \to b$ to obtain the object $(a \xrightarrow{i h} e, z)$ of $(\A/U)_a$. Then going down, we push forward along $k$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$e$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$c+_{a}e$};
\node at (1.2,-0.8) {\Large{$\ulcorner$}};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\psi$} (D);
\end{tikzpicture}
\]
to obtain the object $(c \xrightarrow{\psi} c+_a e, F(\psi)(x))$ of $(\A/U)_c$.  For the other route, first going down, we push the object $(b,x,b \xrightarrow{i} U(x))$ forward along $g \maps b \to d$ by taking the following pushout:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$b$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$d$};
\node (D) at (1.5,-1) {$d+_b e$};
\node at (1.2,-0.8) {\Large{$\ulcorner$}};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(A) edge node[left]{$g$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\phi$} (D);
\end{tikzpicture}
\]
which yields the object $(d \xrightarrow{\phi} d+_b e, F(\phi)(x))$ of $(\A/U)_d$.  Then going left, we precompose with $f \maps c \to d$ to obtain the object $(c \xrightarrow{\phi f} d+_b e, F(\phi)(x))$ of $(\A/U)_c$.

The natural transformation $\theta$ gives a morphism
\[    \theta \maps   (c \xrightarrow{\psi} c+_a e, F(\psi)(x)) \; \to \; (c \xrightarrow{\phi f} d+_b e, F(\phi)(x))  \]
in $(\A/U)_c$.   Concretely, this arises from the universal property of the pushout:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$b$};
\node (B) at (1.5,0) {$e$};
\node (C) at (0,-1) {$d$};
\node (D) at (1.5,-1) {$d+_{b}e$};
\node (E) at (-1.5,0) {$a$};
\node (F) at (-1.5,-1) {$c$};
\node (G) at (2.5,-2) {$c+_{a}e$};
\node at (1.2,-0.8) {\Large{$\ulcorner$}};
\path[->,font=\scriptsize,>=angle 90]
(E) edge node [left] {$k$} (F)
(E) edge node [above] {$h$} (A)
(F) edge node [below] {$f$} (C)
(A) edge node[above]{$i$} (B)
(A) edge node[left]{$g$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\phi$} (D)
(F) edge [bend right] node[below]{$\psi$} (G)
(G) edge [dashed] node[below left]{$\exists ! \;\zeta $} (D)
(B) edge [bend left] (G);
\end{tikzpicture}
\]
Namely, we have $\theta = (1, \zeta, 1)$.   But when the original square in $\A$ (at upper left 
in the diagram above) is a pushout, its pasting with the other pushout gives a pushout, so $\zeta$ and hence $\theta$ is isomorphism.

This shows that $\Phi$ obeys the Beck--Chevalley condition.  Having checked all the hypotheses of \cref{lem:shulman}, we can define $F\lCsp$ to be $\Fr(\Phi)$.
\end{proof}

@@

\begin{defn}
A functor $\Phi \maps \X \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.     
\end{defn}

\begin{defn}
 If $\X$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \maps \X \to \A$ is a bifibration that is also a strict monoidal functor, such that the tensor product of $\A$ preserves cartesian and cocartesian liftings.   Similarly, if $\C$ and $\A$ are symmetric monoidal, a \define{symmetric monoidal} bifibration is a bifibration $\Phi \maps \C \to \A$ that is a symmetric strict monoidal functor.
\end{defn}
